% Reconstruction in LArTPC
% Target length: 30 pages

%----------------------------------------------------------------------------------------------------------------------------------------------------------------------------
\chapter{Reconstruction in a Liquid Argon TPC}\label{chap:LArTPCReconstruction}

{\color{red} Should the title of this chapter reflect more of the original work which is discussed within?  e.g. Shower Reconstrucion in a Liquid Argon TPC?  Although  it is a general reconstruction chapter, everything in Shower Reconstruction in LArTPCs is original.}

The use of LArTPCs in future high-precision projects, such as long-baseline neutrino experiments, is very well motivated by the unprecedented spatial and energy resolution available to detectors utilising the techonology.  In order to take advantage of all this accessible information, accurate reconstruction must be developed to perform pattern recognition and energy determination for use by the proceeding analyses.  The techniques and status of reconstruction in LArTPCs is the subject of this chapter, with particular focus on novel methods developed for the reconstruction of electromagnetic showers.

The implementation of the reconstruction algorithms discussed in this chapter utilises the Liquid Argon Software framework (LArSoft), developed at FNAL and shared between all experiments in the LAr program.  LArSoft will be overviewed in Section~\ref{sec:LArSoft} before the structural and calorimetric reconstructions are discussed in Sections~\ref{sec:ReconstructionChain} and~\ref{sec:Calorimetry} respectively.  The development of new techniques in the reconstruction of showers will compose the main discussion in this chapter and is contained in Section~\ref{sec:ShowerReconstruction}.

%----------------------------------------------------------------------------------------------------------------------------------------------------------------------------
\section{The LArSoft Framework}\label{sec:LArSoft}

LArSoft, yay!

%----------------------------------------------------------------------------------------------------------------------------------------------------------------------------
\section{The Reconstruction Chain}\label{sec:ReconstructionChain}

%----------------------------------------------------------------------------------------------------------------------------------------------------------------------------
\subsection{From Charge to Hits}\label{sec:HitReconstruction}

%----------------------------------------------------------------------------------------------------------------------------------------------------------------------------
\subsection{2D Object Reconstruction}\label{sec:2DReconstruction}

%----------------------------------------------------------------------------------------------------------------------------------------------------------------------------
\subsection{3D Object Reconstruction}\label{sec:3DReconstruction}

%----------------------------------------------------------------------------------------------------------------------------------------------------------------------------
\subsection{Alternative Chains}\label{sec:AlternativeChains}

%----------------------------------------------------------------------------------------------------------------------------------------------------------------------------
\section{Calorimetry Reconstruction}\label{sec:Calorimetry}

%----------------------------------------------------------------------------------------------------------------------------------------------------------------------------
\section{Shower Reconstruction in LArTPCs}\label{sec:ShowerReconstruction}

%----------------------------------------------------------------------------------------------------------------------------------------------------------------------------
\subsection{Showers Overview}\label{sec:ShowersOverview}

%----------------------------------------------------------------------------------------------------------------------------------------------------------------------------
\subsection{BlurredCluster Algorithm}\label{sec:BlurredCluster}

%----------------------------------------------------------------------------------------------------------------------------------------------------------------------------
\subsection{EMShower Algorithm}\label{sec:EMShower}

%----------------------------------------------------------------------------------------------------------------------------------------------------------------------------
\subsection{Track/Shower Separation}\label{sec:TrackShowerSeparation}

%----------------------------------------------------------------------------------------------------------------------------------------------------------------------------
\subsection{Performance of the Reconstruction}\label{sec:ReconstructionPerformance}
